Hemispheric Lateralization and Outcomes After ICH: A Pooled Analysis of Clinical Trials

### 2022-10-07 study protocol.qmd
Update study protocol.qmd

erich.whole <- erich.whole %>%
  mutate(Ethnicity = case_when(
    D21A == "H" ~ "Hispanic or Latino",
    D21A == "N" ~ "Not Hispanic or Latino",
    D21A == "U" ~ "Not Hispanic or Latino"
  ))

@@

erich.whole <- erich.whole %>%
  mutate(symptom.onset = case_when(
    is.na(symptom.onset.date.time) ~ symptom.onset.estimated.date.time,
    TRUE ~ symptom.onset.date.time
  ))

@@

erich.whole <- erich.whole %>%
  mutate(nsgy.evacuation.date = case_when(
    IT5D == "1" ~ ymd_hms(paste(IT5D_DATE, IT5D_TIME)),
    IT5H == "1" ~ ymd_hms(paste(IT5H_DATE, IT5H_TIME)),
    IT5F == "1" ~ ymd_hms(paste(IT5F_DATE, IT5F_TIME))
  ))

@@

# Mortality Status

@@

erich.whole <- erich.whole %>%
  mutate(death.interval = as_date(death.date) - as_date(symptom.onset)) %>%
  as.duration(death.interval)

erich.whole$death.interval <- parse_integer(erich.whole$death.interval)

erich.whole <- erich.whole %>%
  mutate(mrs.90 = case_when(
    death.interval > 90 ~ "6",
    TRUE ~ mrs.90
  ))

>>>>

erich.whole <- erich.whole %>%
  mutate(ethnicity = case_when(
    D21A == "H" ~ "Hispanic or Latino",
    D21A == "N" ~ "Not Hispanic or Latino",
    D21A == "U" ~ "Not Hispanic or Latino"
  ))

@@

erich.whole <- erich.whole %>%
  mutate(symptom.onset.combined = case_when(
    is.na(symptom.onset.date.time) ~ symptom.onset.estimated.date.time,
    TRUE ~ symptom.onset.date.time
  ))

@@

erich.whole <- erich.whole %>%
  mutate(nsgy.evacuation.date.erich = case_when(
    IT5D == "1" ~ ymd_hms(paste(IT5D_DATE, IT5D_TIME)),
    IT5H == "1" ~ ymd_hms(paste(IT5H_DATE, IT5H_TIME)),
    IT5F == "1" ~ ymd_hms(paste(IT5F_DATE, IT5F_TIME))
  ))

erich.whole$nsgy.interval <- as.period(erich.whole$symptom.onset.combined %--% erich.whole$nsgy.evacuation.date.erich)
erich.whole$nsgy.interval <- time_length(erich.whole$nsgy.interval, unit = "days")
erich.whole$nsgy.evacuation.date <- round(erich.whole$nsgy.interval, digits = 0) # Makes it compatabible to merge with ATACH

@@

# Mortality Status and Adding mRS 6

@@

erich.whole$death.interval <- erich.whole$symptom.onset.combined %--% erich.whole$death.date
erich.whole$death.interval <- as.period(erich.whole$death.interval)
erich.whole$death.interval <- time_length(erich.whole$death.interval, unit = "days")

erich.whole <- erich.whole %>%
  mutate(mrs.90 = case_when(
    death.interval < 90 ~ 6,
    TRUE ~ mrs.90
    ))

erich.whole$mrs.90 <- na_if(erich.whole$mrs.90, 8)

erich.whole <- erich.whole %>%
  mutate(mrs.180 = case_when(
    death.interval < 180 ~ 6,
    TRUE ~ mrs.180
    ))

erich.whole <- erich.whole %>%
  mutate(mrs.365 = case_when(
    death.interval < 365 ~ 6,
    TRUE ~ mrs.365
    ))
